Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-29 research_proposal/research_proposal.qmd
expand on the link to alternative estimators

The MinT approach is an algebraical generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is a diagonal or identity matrix, respectively. However, the MinT solution hinges on a reliable estimate of $\boldsymbol{W}_h$. In high-dimensional setting, the usual sample covariance matrix is unstable, thus we need alternative covariance estimators.

@@

@@

and $\hat{\boldsymbol{W}}_1 = \frac{1}{T} \sum_{t=1}^{T} \hat{\boldsymbol{e}}_{t|t-1} \hat{\boldsymbol{e}}_{t|t-1}'$ is the unbiased sample covariance of in-sample one-step-ahead base forecast errors.

>>>>

The MinT approach is an algebraical generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is a diagonal or identity matrix, respectively. However, the MinT solution hinges on a reliable estimate of $\boldsymbol{W}_h$, which is challenging to estimate in high-dimensional setting. Therefore, we need alternative covariance estimators.

@@

We reconstruct estimator of $\boldsymbol{W}_h$ as $\hat{\boldsymbol{W}}_h = k_h \, g(\hat{\boldsymbol{W}}_1)$, and $g(.)$ is an estimator function of the unbiased sample covariance of in-sample one-step-ahead base forecast errors $\hat{\boldsymbol{W}}_1 = \frac{1}{T} \sum_{t=1}^{T} \hat{\boldsymbol{e}}_{t|t-1} \hat{\boldsymbol{e}}_{t|t-1}'$

@@
